### 2020-07-16 paper.tex
write a version of related work

\section{BACKGROUND AND RELATED WORK}

@@

Let $f : Z \to Z$ denote an involution ($f^{-1} = f$) such that the pushforward of $\mu$ under $f$, denoted $\mu \circ f^{-1}$, is absolutely continuous with respect to $\mu$, with Radon-Nikodym derivative $d (\mu \circ f^{-1}) / d\mu : Z \to [0, \infty)$. Involutive MCMC runs $f$ on $(x, y)$ to obtain $(x', y')$, then computes an acceptance probability $\alpha$.
With probability $\alpha$, the new state $x'$ is returned; otherwise, the previous state $x$ is repeated.
%Let $y \sim q_x(\cdot)$ denote a random sample from the measure defined by $A \mapsto \int_A q_x(y) \mu_Q(dy)$ for $A \in \Sigma_Q$.

@@

\begin{algorithm}[h]
\begin{algorithmic}
\Procedure{involutive-mcmc}{$p$, $q$, $f$, $x$}
    \State $y \sim q_x(\cdot)$ \Comment{Sample auxiliary state}
    \State $(x', y') \gets f(x, y)$ \Comment{Apply involution}
    \State $\alpha \gets
        \displaystyle \frac{p(x') q_{x'}(y')}{p(x) q_{x}(y)} \cdot \left( \frac{d (\mu \circ f^{-1})}{d \mu} (x, y)\right)$
    \State $r \sim \mathrm{Uniform}(0, 1)$
    \State \algorithmicif \, $r \le \alpha$ \algorithmicthen \, \Return $x'$ \algorithmicelse \, \Return $x$ 
\EndProcedure
\end{algorithmic}
\caption{Involutive MCMC}
\label{alg:involutive-mcmc}
\end{algorithm}

>>>>

\section{RELATED WORK}

The involutive MCMC construction was previously implemented~\citep{gen-inv-mcmc} by the authors as part of the inference library of the Gen probabilistic programming system~\citep{cusumano2019gen}.
The construction was motivated in part by a desire for a simple interface that automated the implementation of reversible jump MCMC samplers~\citep{green1995reversible}, state-dependent mixtures of proposals on complex state spaces, and data-driven neural proposals.
Gen's involutive MCMC construction has since been used by a number of researchers to design and implement MCMC algorithms in diverse domains including computational biology~\citep{merrell2020inferring} and artificial intelligence~\citep{zhi2020online}.

\citet{imcmc} independently identified the involutive MCMC construction as a unifying framework for MCMC algorithms, and showed how a number of classic and recent MCMC algorithms can be cast within this framework.
\citet{imcmc} also identified design principles for developing new MCMC algorithms using the involutive MCMC construction, and showed that the framework aids in the derivation of novel efficient MCMC algorithms.

The involutive MCMC construction encompasses many existing classes of MCMC kernels, some of which explicitly make use of bijective or involutive deterministic maps.
In particular, the reversible jump framework~\citep{green1995reversible,hastie2012model} employs a family of continuously differentiable bijections between the Euclidean parameter spaces of different models.
\citet{tierney1998note} described a family of deterministic proposals based on a deterministic involution that is equivalent to involutive MCMC but without the auxiliary proposal distribution.
More recently,~\citet{spanbauer2020deep} defined a class of deep generative model based on differentiable involutions and trained these models to serve as efficient proposal distributions on continuous state spaces; the resulting algorithm is an instance of the construction presented in this paper.
%Gen~\citet{cusumano2019gen}
%Gen's involution MCMC construct~\citet{gen-inv-mcmc}
%Reversible jump MCMC~\citet{green1995reversible}
%^Using probabilistic programs as proposals~\citet{cusumano2018using}
%Reversible jump probabilistic programming~\citet{roberts2019reversible}

@@

Let $f : Z \to Z$ denote an involution ($f^{-1} = f$) such that the pushforward of $\mu$ under $f$, denoted $\mu \circ f^{-1}$, is absolutely continuous with respect to $\mu$, with Radon-Nikodym derivative $d (\mu \circ f^{-1}) / d\mu : Z \to [0, \infty)$. Involutive MCMC runs $f$ on $(x, y)$ to obtain $(x', y')$, then computes an acceptance probability $\alpha$.
With probability $\alpha$, the new state $x'$ is returned; otherwise, the previous state $x$ is repeated.
%Let $y \sim q_x(\cdot)$ denote a random sample from the measure defined by $A \mapsto \int_A q_x(y) \mu_Q(dy)$ for $A \in \Sigma_Q$.
\begin{algorithm}[h]
\begin{algorithmic}
\Procedure{involutive-mcmc}{$p$, $q$, $f$, $x$}
    \State $y \sim q_x(\cdot)$ \Comment{Sample auxiliary state}
    \State $(x', y') \gets f(x, y)$ \Comment{Apply involution}
    \State $\alpha \gets
        \displaystyle \frac{p(x') q_{x'}(y')}{p(x) q_{x}(y)} \cdot \left( \frac{d (\mu \circ f^{-1})}{d \mu} (x, y)\right)$
    \State $r \sim \mathrm{Uniform}(0, 1)$
    \State \algorithmicif \, $r \le \alpha$ \algorithmicthen \, \Return $x'$ \algorithmicelse \, \Return $x$ 
\EndProcedure
\end{algorithmic}
\caption{Involutive MCMC}
\label{alg:involutive-mcmc}
\end{algorithm}

@@
